Supplementary Figure 5c

### 2018-05-16 inst/figure3c/figure3c.Rmd
syncing methods in paper and Rmds for fig3c and supp fig5c

Three technical triplicates and three biological replicates were included in each experiment and these were independantly normalized for each condition to the 0 time point afterwhich the mean was calculated for the technical replicates. A polynomial regression model was then implemented separatley for each culture condition. with the mean of the technical replicates as the dependant variable and time and cell line as the independant variables.

@@

<div class="caption">
The effects of miR34a asRNA overexpression on growth in normal and starvation conditions in the PC3 prostate cancer cell line. Fold confluency (% confluency / Time 0 % confluency) is indicated on the y-axis. Colored lines indicate the polynomial regression model where mean fold confluency from 3 independant experiments is the dependant variable and time and cell line are independant variables. The grey shadows illustrate the 95% confidence interval for the regression. Estimates, standard error (std.error), and P values for the cell line covariate for each model are indicated in the upper left hand corner.
</div>

>>>>

Fold confluency was then calculated as % confluency / % confluency time 0 for each condition and the mean of the 3 technical replicates was subsequently calculated for each of the 3 biological replicates. A polynomial regression model was then constructed modeling the fold confluency as the dependent variable and time and cell line as independent variables. Reported P values are derived from the t-test, testing the null hypothesis that the coefficient estimate of the cell line covariate is equal to 0.

@@

<div class="caption">
The effects of miR34a asRNA overexpression on growth in normal and starvation conditions in the PC3 prostate cancer cell line. Fold confluency (% confluency / Time 0 % confluency) is indicated on the y-axis. Colored lines indicate the polynomial regression model where mean fold confluency from 3 independent experiments was modeled as a function of time and cell line. The grey shadows illustrate the 95% confidence interval for the regression. Estimates, standard error (std.error), and P values for the cell line covariate for each model are indicated in the upper left hand corner.
</div>

### 2018-05-16 inst/supp_figure5c/supp_figure5c.Rmd
syncing methods in paper and Rmds for fig3c and supp fig5c

20^4 PC3 cells, either miR34a asRNA overexpressing or mock, were harvested and stained in 1 ml PBS with 5uM CellTrace Violet (Invitrogen) for 5min and subsequently seeded in 12 well plates. Time 0 measurements were taken once cells had attatched and treatments with RPMI (Gibco, life technology) 10% FBS, RPMI 0.1% FBS, or HBSS were simultaniously initiated in the remaining cells. RPMI mediums were all additionally supplemented with 2mM L-glutamine and 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum. Cells were incubated for the indicated times before harvesting and CellTrace Violet was quantified via flow cytometry (Sony SH800S Cell Sorter). Time 0 was performed in biological triplicate and technical duplicate whereas all other time points were performed in biological triplicates with one technical replicate.

@@

Each replicate and condition were subsampled so that each had a total of 10000 cells. The mean of each technical replicate for time point 0 was calculated and, subsequently, the time 0 flouresence intensity was subtracted from each sample. The mean difference in flouresence intensity was then calculated for each biological replicate and condition and used to build a polynomial model per condition (i.e. RPMI, 0.1% FBS, and HBSS).

>>>>

PC3 stable cell lines, either miR34a asRNA overexpressing or mock, were harvested and stained in 1 ml PBS with 5uM CellTrace Violet for 5 minutes and subsequently seeded in 12 well plates at 2 x 104 cells per well. Time 0 measurements were taken once cells had attached and treatments with RPMI (Gibco, life technology) 10% FBS, RPMI 0.1% FBS, or HBSS were simultaneously initiated in the remaining cells. RPMI mediums were all additionally supplemented with 2mM L-glutamine and 50ug/ml Penicillin-Streptomycin. Cells were incubated for the indicated times before harvesting and CellTrace Violet was quantified via flow cytometry (Sony SH800S Cell Sorter). Time 0 was performed in biological triplicate and technical duplicate whereas all other time points were performed in biological triplicates with one technical replicate.

@@

Analysis was performed by first, subsampling each replicate and condition so that each had a total of 10000 cells. The mean of each technical replicate for time point 0 was calculated and, subsequently, the time 0 fluorescence intensity was subtracted from each sample. The mean difference in fluorescence intensity was then calculated for each biological replicate and condition and used to build a polynomial regression model per condition (i.e. RPMI, 0.1% FBS, and HBSS) where difference in fluorescence intensity was modeled as a function of time and cell line. Reported P values are derived from the t-test, testing the null hypothesis that the coefficient estimate of the cell line covariate is equal to 0.
